Model LF

### 2022-12-20 paper version 2.Rmd
Commit

COMMENT> Disposable income (redundant for now)
IDENTITY> yd_h1
EQ> yd_h1 = yh_h + tax_h + nben_h

@@

@@

```{r}
###Gengivelse af stød til model
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur

ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk

ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_bs3 = Shock_bs3$simulation$yk
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un
prodk_bs3 = Shock_bs3$simulation$prodk
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio
lf_bs3 = Shock_bs3$simulation$lf
nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation
y_bs3 = Shock_bs3$simulation$y
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock

ur_bs3 = Shock_bs3$simulation$ur
```

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person

ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
```

@@

```{r}
###Gengivelse af stød til model
y_03 = Shock_3$simulation$y
yk_03 = Shock_3$simulation$yk
yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
nben_h_un_03 = Shock_3$simulation$nben_h_un
ur_03 = Shock_3$simulation$ur
prodk_03 = Shock_3$simulation$prodk
```

>>>>

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> g
EQ> g = g*1

@@

```{r}
###Gengivelse af stød til model
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur
s_g_bs1 = Shock_bs1$simulation$s_g
yh_g_bs1 = Shock_bs1$simulation$yh_g
i_g_bs1 = Shock_bs1$simulation$i_g
ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk
yd_g_bs1 = Shock_bs1$simulation$yd_g
tax_g_bs1 = Shock_bs1$simulation$tax_g
w_h_r_bs1 = Shock_bs1$simulation$w_h_r
tax_h_bs1 = Shock_bs1$simulation$tax_h
tax_g
nben_g_bs1 = Shock_bs1$simulation$nben_g
ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_bs3 = Shock_bs3$simulation$yk
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un
prodk_bs3 = Shock_bs3$simulation$prodk
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio
lf_bs3 = Shock_bs3$simulation$lf
nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation
y_bs3 = Shock_bs3$simulation$y
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock
s_g_bs3 = Shock_bs3$simulation$s_g
i_g_bs3 = Shock_bs3$simulation$i_g
yd_g_bs3 = Shock_bs3$simulation$yd_g
ur_bs3 = Shock_bs3$simulation$ur
nben_g_bs3 = Shock_bs3$simulation$nben_g
nsben_h_bs3 = Shock_bs3$simulation$nsben_h
```

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
w_h_r
```

```{r, fig.width=8, fig.height=8}
par(mfrow=c(2,2))

plot(yd_g_01-yd_g_bs1, col= "red")
plot(tax_g_01-tax_g_bs1, col= "red")
plot(tax_h_01-tax_h_bs1, col= "red")
plot(nben_g_01 -nben_g_bs1, col= "red")

plot(nben_h_un_01 - nben_h_un_bs1, col= "red")

plot(w_h_r_01 - w_h_r_bs1, col= "red")
```

```{r, fig.width=8, fig.height=6}

plot((s_g_01- s_g_bs1), col= "red")

plot((i_g_01 - i_g_bs1), col= "red")

plot(yd_g_01-yd_g_bs1, col= "red")
plot(yh_g_01-yh_g_bs1, col= "red")
plot(tax_g_01-tax_g_bs1, col= "red")
plot(nben_g_01 - nben_g_bs1, col= "red")

plot(nsben_h_01 - nsben_h_bs1, col= "red")

plot(nben_h_un_01 - nben_h_un_bs1, col= "red")
```

@@

```{r}
###Gengivelse af stød til model
y_03 = Shock_3$simulation$y
yk_03 = Shock_3$simulation$yk
yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
nben_h_un_03 = Shock_3$simulation$nben_h_un
ur_03 = Shock_3$simulation$ur
prodk_03 = Shock_3$simulation$prodk
s_g_03 = Shock_3$simulation$s_g
i_g_03 = Shock_3$simulation$i_g
yd_g_03 = Shock_3$simulation$yd_g
nben_g
nben_g_03 = Shock_3$simulation$nben_g
nsben_h

nsben_h_03 = Shock_3$simulation$nsben_h
```

```{r, fig.width=10, fig.height=8}
par(mfrow=c(2,2))
plot((s_g_03- s_g_bs3), col= "red")

plot((i_g_03 - i_g_bs3), col= "red")

plot(yd_g_03-yd_g_bs3, col= "red")

plot(nben_g_03 - nben_g_bs3, col= "red")

plot(nsben_h_03 - nsben_h_bs3, col= "red")

plot(nben_h_un_03 - nben_h_un_bs3, col= "red")
```
